### 2022-11-12 NSF2022/Description/backgroundv2.tex
BG mods

Mathematical models of self-organization encompasses a broad range of
interesting and challenging phenomena. For example, understanding the
organization of lipids and proteins in vesicles is crucial to design
effective drug and vaccine carriers. The COVID-19 pandemic has led to an
unprecedented and concerted worldwide effort in biophysical modeling of
the mechanisms of RNA condensation by structural proteins, protein
oligomerization, and cellular membrane–protein interactions that
ultimately control virus structure, in an effort to curtail pathogens
like the Severe Acute Respiratory Syndrome Coronavirus 2. Using powerful
capillary and van der Waals forces that exist at the nanoscale,
engineers have developed superior techniques to print high-resolution,
nanoscale features on devices like sensors, lasers, and LEDs. Finally,
researchers have introduced data-driven methods to study complex
patterns that emerge in particle and agent-based systems like swarms and
flocking.

A number of mathematical techniques have been developed to handle
self-organizing systems. Each technique has its advantages and
disadvantages. Prominent in chemistry and biology, molecular dynamics
(MD) simulations offers unparalleled resolution of protein-lipid
interactions, say, but because of the large number of non-linear
interactions involved, is limited to short time and small spatial
scales. In terms of inverse problems, agent based systems also involve
relatively large numbers of particles and researchers extensively
consider the problem of using trajectory data to learn interaction
kernels of the dynamics when constrained to evolve on Riemannian
manifolds. Once the interaction kernels are known, one can in principle
derive partial differential equations (PDE) for the macroscopic
behavior.

The phase field method and self-consistent field theory are popular
approaches to self-organization in Applied Mathematics. Motivated by
Ginzburg-Landau theory, these methods introduce a scalar-valued phase
field function for the volume fraction of lipids and water in modeling
vesicles membranes, for example. Sometimes called diffuse interface
methods, one devises energy functionals involving the gradient and
well-potentials of the phase field, and possibly long range interaction
kernels, that yield approximate mathematical surfaces of almost
arbitrary topology. Because the fluid interfaces are given by the
level-set of a smooth function, the evolution equations can be studied
by well-established tools like variational methods and regularity
theory, and are amenable to numerical approximation. On the downside,
granular details like the shape changes of a protein, for example, are
clumsy to incorporate in the model. Moreover, numerical simulations of
phase field models typically discretize the entire fluid domain under
consideration, and apply cutoff boundary conditions when periodic
domains are not under consideration.

@@

\subsection{Problem formulation}
Recently, we have developed a new mathematical model of
self-organization~\cite{FuQuRyYo22,fu-ryh-qua-you2022,Fu2018_SIAM}. The
model takes ideas from the phase field method and leverages boundary
integral equations to resolve complex domains and speed up computations.
To formulate the problem, consider a collection of $N_b$-many rigid
bodies $U_i(t) \subset \RR^n$ with boundary $\Gamma_i(t)$. We call these
bodies ``granules''. The granules are immersed in an incompressible,
zero-Reynolds number fluid $\Omega(t) = \RR^n \setminus \cup_{i=1}^{N_b}
U_i(t)$ (Figure~\ref{fig:flow_map}).

We look for $N_b$-many rigid body transformations
\begin{align}
\label{eq:RBT}
  F_i(\XX,t) = R_i(t)(\XX - \aa_i(0)) + \aa_i(t),\quad \XX \in U_i(0),
\end{align}
where $i = 1,\ldots,N_b,$ $R_i(t)$ is a rotation (proper orthogonal) $n
\times n$ matrix, $\aa_i(t)$ are the granule centers, and $\XX$ is a
reference coordinate. The transformations~\eqref{eq:RBT} determine how
the granules move through space. Throughout, $\nnu$ refers to unit
normal pointing into $\Omega(t)$ (Figure~\ref{fig:flow_map}).

The key idea is to define the dynamics using the following boundary
value problem system:
\begin{alignat}{4}
  \label{eqn:stokes} 
  -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
  \quad \nabla \cdot \uu = 0, &&\xx \in \Omega(t), \\
  \label{eqn:phase}
  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, &&\xx \in \Omega(t),\\
  \label{eqn:noslip}        
  \frac{dF_i}{dt}(\XX,t) & = \uu(\xx) = 
    \vv_i + \omega_i \times (\xx - \aa_i), 
  \quad &&\xx \in \Gamma_i(t),\\
  \label{eqn:material}
  \phi(\xx) &= h_i(\XX),  &&\xx \in \Gamma_i(t),
\end{alignat}
for $i=1,\ldots,N_b$ and where $\xx = F_i(\XX,t)$.  Finally,
\begin{align}
\label{eqn:stressbalance}
\int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif s = \mathbf{0},\quad
\int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu \,\dif s = \mathbf{0}
\end{align}
where
\begin{align}
\label{eqn:hydro_stress}
\sigma = \mu(\nabla \uu + \nabla \uu^T) - pI,\quad 
T_i = \gamma\left[\epsilon^{-1} W'(\phi)I
  + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
  \phi^T\right)\right]
\end{align}
are the hydrodynamic and phase stresses, respectively; $I$ is the
$n\times n$ identity matrix. For vectors $\aa, \bb \in \mathbb{R}^2$,
we follow the usual convention of defining the ``cross product'' as $\aa
\times \bb = (\aa^{\perp} \cdot \bb) \kk$ where $\kk = (0,0,1) \in
\RR^3$ and $(a_1,a_2)^{\perp} = (-a_2,a_1)$.

The above form a semi-linear elliptic system for evolution of the
granules. Equation~\eqref{eqn:stokes} is the Stokes equations that
describes the velocity $\uu$ and pressure $p$ of the aqueous region with
viscosity $\mu$. Equation~\eqref{eqn:phase} describes the phase
transitions of the scalar order parameter $\phi$ with a decay length
$\epsilon$. The scalar function $W(\phi)$ is a nonnegative well
potential where the local minima represent metastable states $\phi_0,
\phi_1,\ldots$ of the water phase. To have finite bulk energy, the
minimum potential phase $\phi_0$ has $W(\phi_0) = 0$. Mathematically,
this order parameter is responsible for the attraction and adhesion
between granules that want to align boundaries of like phase.

The next three equations are the moving domain boundary conditions.
Equations~\eqref{eqn:noslip} specify a no-slip boundary condition for a
rigid body with translation velocity $\aa'_i(t) = \vv_i$ and angular
velocity $\omega_i$ about the point $\aa_i(t) \in U_i(t)$. ($\omega_i$
is the axial vector of the skew symmetric matrix $R'_i(t)$.) In
equation~\eqref{eqn:material}, the function $h_i$ is a material label
specifying the phases at water-granule interface. The boundary condition
for $\phi$ is transported by the flow and satisfies $\phi_t + \uu \cdot
\nabla \phi = 0$ on $\Gamma_i$. Finally,
equation~\eqref{eqn:stressbalance} closes the system by requiring that
the force and torque generated by hydrodynamic stress balances that
generated by phase stress $T_i$ in~\eqref{eqn:hydro_stress}. The
parameter $\gamma > 0$ is surface tension.

@@

Computational methods to solve the PDEs~\eqref{eqn:stokes}
and~\eqref{eqn:phase} are challenging to develop because of the complex
and unbounded domain. This challenge is compounded when dense
suspensions are considered. Integral equations (IEs) offer an
alternative formulation of the PDEs that only require meshing the
boundary of the granules rather than all of $\Omega(t)$
(Figure~\ref{fig:fem_vs_bie}), and the automatically satisfy far field
conditions. Additional advantages of an discretizations of IE
formulations include high-order, or even spectral, accuracy and
well-conditioned linear system that can be solved iteratively with a
mesh-independent number of Krylov iterations such as the generalized
minimal residual method (GMRES). However, IEs have challenges: nearly
touching granules requires a quadrature rule for nearly-singular
integrals; their discretization results in dense matrices; and they
cannot immediately be applied to non-linear PDEs. The IE community,
including PI Quaife, has developed a variety of tools to address these
numerical challenges, and we discuss our planned approach in
Section~\ref{sec:specificaim2}.

In the absence of external flow, the
system~\eqref{eq:RBT}--\eqref{eqn:stressbalance} has the energy law
\begin{align}
\label{eq:energy_law}
  \frac{d}{dt}E
  = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2 \,d\xx,\quad
    E = \gamma \int_{\Omega(t)}
  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
\end{align}
Here $E$ is the energy stored in the phase transitions. Mathematically,
the energy law states that changes in granule configuration
instantaneously change the phase energy $E$. The dynamics are such that
the change energy is lost due to hydrodynamic dissipation. Further
details and generalizations are provided in \S\ref{sec:specific_aim1}
and \S\ref{subsec:specific_aim_3}. Because $E$ depends both on $\phi$
and $\Omega(t)$, the derivation of~\eqref{eq:energy_law} is somewhat
subtle and has been worked out in detail in~\cite{Fu2018_SIAM}. The
calculation uses the Rayleigh Transport Theorem to write the time
derivative of $E$ as an energy density flux involving the phase stress
$T_i$ on the boundary, and a bulk term involving the Euler-Lagrange
derivative of $E$. The Euler-Lagrange derivative vanishes due
to~\eqref{eqn:phase} and the boundary flux transforms into viscous
dissipation due to~\eqref{eqn:hydro_stress} and the Stokes equations.

%It goes as follows. Using the Rayleigh Transport Theorem, the time
%derivative out $E$ yields an energy density flux involving the phase
%stress $T_i$ at the boundary, plus a bulk term involving the
%Euler-Lagrange derivative of $E$.

In the far field, $\lim_{\xx \to \infty} \phi(\xx) = \phi_0$ and for the
background flow, we require that $\lim_{\xx \to \infty} \uu(\xx) -
\uu_{\infty}(\xx) = \mathbf{0}$. In the case of shear background flow,
for example,
\begin{align}
\label{eqn:shear_BG_flow}
\uu_{\infty}(\xx) = \dot{\gamma} \xx \cdot \mathbf{e}_y \mathbf{e}_x,
\end{align}
where $\dot \gamma$ is the shear rate and $\mathbf{e}_x$, $\mathbf{e}_y$
are horizontal and vertical basis vectors, respectively. Other
background flows include extensional, parabolic Poiseuille, and
Taylor-Green flow. For numerical stability and physical realism, we
introduce pairwise repulsive forces and torques
in~\eqref{eqn:stressbalance} to prevent the collision between
neighboring granules. We include the repulsive potential in the energy
law~\eqref{eq:energy_law}. A background flow adds elastic energy to the
granule configurations and is quantified by simulation. We refer to the
PIs work~\cite{FuQuRyYo22, fu-ryh-qua-you2022, Fu2018_SIAM} for details.

@@

Finally, in terms of mathematical justifications, we mention that in the
single-well case $W(\phi) = \tfrac{1}{2}\phi^2$, equation
\eqref{eqn:phase} takes the form of a screened Laplace equation
$-\epsilon^2 \Delta \phi + \phi =0$. For a fixed domain $\Omega$ with
class $\mathbf{C}^2$ boundary~\cite{}, if the material label $h_i = 1$
everywhere, then $\phi$ has a boundary layer going from $1$ at the
boundary to $0$ in the bulk and one can prove that 
\begin{align}
\label{eqn:math_motivation}
\lim_{\epsilon \to 0} E = \frac{\gamma}{2} \int_{\partial \Omega} 1 \,dS.
\end{align}
In other words, the phase energy can be viewed as an approximation of
surface energy that ``extends'' into the bulk. In the general case,
$h_i^2$ replaces $1$ in~\eqref{eqn:math_motivation}. We are confident
that~\eqref{eq:RBT}--\eqref{eqn:stressbalance} is a correct description
of long-range interactions between granule surfaces.

@@

\subsection{Applications}
Since the formulation is scale independent, it can be applied broad
range of nonspecific self-organization phenomena in surface chemistry,
biology and engineering. For one, the
formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
the right behavior expected from amphiphilic self-assembly. For example,
three bodies with amphiphilic label (\S\ref{sec:specific_aim1})
spontaneously self-organize to sequester the hydrophobic fluid phase
(the red phase in Figure~\ref{fig:flow_map}).  Moreover, a simple change
of boundary conditions from amphiphilic, to biased hydrophobic, to polar
results in distinct equilibrium morphologies
(Figure~\ref{fig:self-assembly2}). (i) Chemistry: Janus spheres Since
the formulation is scale independent, it can represent a suspension of
amphiphiles, where the granules represent the mean properties of a small
collection of lipids, at the nanoscopic scale. For larger scales, the
representation is literal and the granules Janus spheres. (ii) Pickering
emulsion (iii) \todo[inline]{Bertozzi's problem} (iv) Tension driven
microprinting (v) Vesicle hydrodynamics.

>>>>

Self-organization encompasses a broad range of
interesting and challenging phenomena in engineering and science.
For example, understanding the
organization of lipids and proteins in vesicles is crucial to design
effective drug carriers
and functional mimics of cell membranes
\cite{Marui2022IncreasedEO,https://doi.org/10.1002/adma.202206288}.
The COVID-19 pandemic has led to a
concerted, worldwide efforts to understand
the mechanisms of RNA condensation by structural proteins protein
oligomerization that control virus structure
\cite{Kim2021SelfassembledMV}.
Engineers have developed superior techniques
that rely on nanoscale  
capillary and van der Waals forces
to print high-resolution
features on devices \cite{Zeng20223DprintedMT}.
Finally, researchers design efficient algorithms for
constructing for the interaction kernels to study complex
patterns in agent-based systems like swarms and flocking
\cite{Lu2019NonparametricIO,Tadmor2021OnTM}.

%A number of mathematical techniques have been developed to handle
%self-organizing systems. Each technique has its advantages and
%disadvantages. Prominent in chemistry and biology, molecular dynamics
%(MD) simulations offers unparalleled resolution of protein-lipid
%interactions, say, but because of the large number of non-linear
%interactions involved, is limited to short time and small spatial
%scales. In terms of inverse problems, agent based systems also involve
%relatively large numbers of particles and researchers extensively
%consider the problem of using trajectory data to learn interaction
%kernels of the dynamics when constrained to evolve on Riemannian
%manifolds. Once the interaction kernels are known, one can in principle
%derive partial differential equations (PDE) for the macroscopic
%behavior.

When fluids are involved,
tracking self-organization
becomes difficult due to the deformability of
suspended media.  A dominant approach in this area,
the phase field method
introduce a scalar-valued phase
field function for the volume fraction of
amphiphilic lipids or polymers in solvent, for example.
Sometimes called diffuse interface
methods, one devises energy functionals involving the gradient and
well-potentials of the phase field, and possibly long range interaction
kernels, 
\cite{Promislow2022UndulatedBI,C9SM01983A,doi:10.1063/5.0009734,
LiAn-Chang16,Choksi2003OnTD}.
Because the fluid interfaces are given by the
level-set of a smooth function,
they can have almost arbitrary topology
e.g., free ends, junctions
\cite{Promislow2017ExistenceBA,Promislow2022UndulatedBI},
the evolution equations can be studied
by well-established tools variational and analytical means,
\cite{Gavish2011CurvatureDF,Dai2019WeakSF,Dai2015CompetitiveGE,
Dai2022GeometricEO,Dai2020MinimizersFT,Dai2013GeometricEO},
and the governing equations are amenable to numerical approximation
\cite{Christlieb2020BenchmarkCO,Christlieb2019CompetitionAC}.
One of the downsides, though, 
is that granular details like molecular orientations and
shape changes induced by proteins that may be crucial to the physics, are
clumsy to incorporate in the model. Moreover, numerical simulations of
phase field models typically discretize the entire fluid domain under
consideration, and apply cutoff boundary conditions when periodic
domains are not under consideration.

@@

\subsection{Problem formulation}
We recently developed a new mathematical model of
self-organization~\cite{FuQuRyYo22,fu-ryh-qua-you2022,Fu2018_SIAM}.
It takes ideas from the phase field method and leverages boundary
integral equations to resolve complex domains and speed up computations.
To formulate the problem, consider a collection of $N_b$-many rigid
bodies $U_i(t) \subset \RR^n$ with boundary $\Gamma_i(t)$. We call these
bodies ``granules''. The granules are immersed in an incompressible,
zero-Reynolds number fluid $\Omega(t) = \RR^n \setminus \cup_{i=1}^{N_b}
U_i(t)$ (Figure~\ref{fig:flow_map}).
Throughout, $\nnu$ refers to unit
normal pointing into $\Omega(t)$ (Figure~\ref{fig:flow_map}).

To determine how the granules move through space,
we look for rigid body transformations
\begin{align}
\label{eq:RBT}
  F_i(\XX,t) = R_i(t)(\XX - \aa_i(0)) + \aa_i(t),\quad \XX \in U_i(0),
\end{align}
where $i = 1,\ldots,N_b,$ $R_i(t)$ is a rotation (proper orthogonal) $n
\times n$ matrix, $\aa_i(t)$ are the granule centers, and $\XX$ is a
reference coordinate.
The dynamics come from the following system of semi-linear, elliptic boundary value problems:
\begin{alignat}{4}
  \label{eqn:stokes} 
  -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
  \quad \nabla \cdot \uu = 0, &&\xx \in \Omega(t), \\
  \label{eqn:phase}
  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, &&\xx \in \Omega(t),\\
  \label{eqn:noslip}        
  \frac{dF_i}{dt}(\XX,t) & = \uu(\xx) = 
    \vv_i + \omega_i \times (\xx - \aa_i), 
  \quad &&\xx \in \Gamma_i(t),\\
  \label{eqn:material}
  \phi(\xx) &= h_i(\XX),  &&\xx \in \Gamma_i(t),
\end{alignat}
for $i=1,\ldots,N_b$ and where $\xx = F_i(\XX,t)$.  Finally,
\begin{align}
\label{eqn:stressbalance}
\int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif s = \mathbf{0},\quad
\int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu \,\dif s = \mathbf{0}
\end{align}
where
\begin{align}
\label{eqn:hydro_stress}
\sigma = \mu(\nabla \uu + \nabla \uu^T) - pI,\quad 
T_i = \gamma\left[\epsilon^{-1} W'(\phi)I
  + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
  \phi^T\right)\right]
\end{align}
are the hydrodynamic and phase field stresses, respectively.
Equation~\eqref{eqn:stokes} is the Stokes equations 
describing the velocity $\uu$ and pressure $p$ of the aqueous region with
viscosity $\mu$.
Equation~\eqref{eqn:phase} describes the
transitions of the scalar order parameter $\phi$ with a decay length
$\epsilon$.
The scalar function $W(\phi) : \mathbb{R} \to \mathbb{R}$ is a nonnegative
well-potential with local minima $\phi_0, \phi_1$  etc.
representing metastable states of the solvent.
For the single well case, $W(\phi) = \frac{1}{2}\phi^2$
has the minimum $\phi_0 = 0$ and the phase field equation
\eqref{eqn:phase} becomes the \emph{linear} screened Laplace equation.
For the double well case e.g, $W(\phi) = \frac{1}{4}(\phi^2-1)^2+cx$, $c > 0$,
the phase field equation \eqref{eqn:phase} takes the form of an
Allen-Cahn equation with local minima $\phi_0 < 0 < \phi_1$.
Section \ref{sec:specific_aim1} discusses certain
modifications needed for \eqref{eqn:phase} in the nonlinear case.

For the moving domain boundary conditions,
equations~\eqref{eqn:noslip} specify a no-slip boundary condition for a
rigid body with translation velocity $\aa'_i(t) = \vv_i$ and angular
velocity $\omega_i$ (the axial vector for $R'_i(t)R_i(t)^T$)
about the point $\aa_i(t) \in U_i(t)$. In
equation~\eqref{eqn:material}, the function $h_i$ is a material label
specifying the phase at water-granule interface.
Finally, equation~\eqref{eqn:stressbalance} closes the system by requiring that
the force and torque generated by hydrodynamic stress balances that
generated by phase stress $T_i$ in~\eqref{eqn:hydro_stress}. The
parameter $\gamma > 0$ is surface tension,
$I$ is the $n\times n$ identity matrix,
and we define the ``cross product'' as
$\aa \times \bb = (\aa^{\perp} \cdot \bb) \kk$ where $\kk = (0,0,1) \in
\RR^3$ and $(a_1,a_2)^{\perp} = (-a_2,a_1)$ when $\aa, \bb \in \mathbb{R}^2$.

@@

Computational methods to solve the PDEs~\eqref{eqn:stokes}
and~\eqref{eqn:phase} are challenging to develop because of
the complicated and unbounded domain.
This challenge is compounded when dense
suspensions are considered. Integral equations (IEs) offer an
alternative formulation of the PDEs that only require meshing the
boundary of the granules rather than all of $\Omega(t)$
(Figure~\ref{fig:fem_vs_bie}), and the automatically satisfy far field
conditions. Additional advantages of an discretizations of IE
formulations include high-order, or even spectral, accuracy and
well-conditioned linear system that can be solved iteratively with a
mesh-independent number of Krylov iterations such as the generalized
minimal residual method (GMRES). However, IEs have challenges: nearly
touching granules requires a quadrature rule for nearly-singular
integrals; their discretization results in dense matrices; and they
cannot immediately be applied to non-linear PDEs. The IE community,
including PI Quaife, has developed a variety of tools to address these
numerical challenges, and we discuss our planned approach in
Section~\ref{sec:specificaim2}.

In the absence of external flow, the
system~\eqref{eq:RBT}--\eqref{eqn:stressbalance} has the energy law
\begin{align}
\label{eq:energy_law}
  \frac{d}{dt}E
  = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2 \,d\xx,\quad
    E = \gamma \int_{\Omega(t)}
  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
\end{align}
Here $E$ is the energy stored in the phase transitions
and the energy law states that
the granules move to decrease energy,
which is lost due to viscous dissipation.
The derivation of \eqref{eq:energy_law} is interesting
because $E$ depends both on $\phi$
and $\Omega(t)$. It uses the Rayleigh Transport Theorem to write the time
derivative of $E$ as an energy density flux through the boundary
involving the phase stress $T_i$, and a bulk term involving the Euler-Lagrange
derivative of $E$~\cite{Fu2018_SIAM}. The Euler-Lagrange derivative vanishes due
to~\eqref{eqn:phase} and the boundary flux transforms into viscous
dissipation due to~\eqref{eqn:hydro_stress} and the Stokes equations.

In the far field, $\lim_{\xx \to \infty} \phi(\xx) = \phi_0$ and for the
background flow, we require that $\lim_{\xx \to \infty} \uu(\xx) -
\uu_{\infty}(\xx) = \mathbf{0}$, where
the background flow takes the form
%In the case of shear background flow,
%for example,
%\begin{align}
%\label{eqn:shear_BG_flow}
%\uu_{\infty}(\xx) = \dot{\gamma} \xx \cdot \mathbf{e}_y \mathbf{e}_x,
%\end{align}
%where $\dot \gamma$ is the shear rate and $\mathbf{e}_x$, $\mathbf{e}_y$
%are horizontal and vertical basis vectors, respectively.
%Other
%background flows include
shear, extensional, parabolic Poiseuille, and
Taylor-Green flow, for example.
For numerical stability and physical realism, we
include pairwise repulsive forces and torques
in~\eqref{eqn:stressbalance} to prevent the collision between
neighboring granules which introduces a repulsive potential in the energy
law~\eqref{eq:energy_law}. Background flow adds elastic energy to the
granule configurations.
%and is quantified by simulation. We refer to the
%PIs work~\cite{FuQuRyYo22, fu-ryh-qua-you2022, Fu2018_SIAM} for details.

@@

In terms of mathematical justifications, we mention that when
equation \eqref{eqn:phase} takes the form of a screened Laplace equation
$-\epsilon^2 \Delta \phi + \phi =0$, for a fixed domain $\Omega$ with
smooth boundary, if the material label $h_i = 1$
everywhere, then $\phi$ has a boundary layer going from $1$ at the
boundary to $0$ in the bulk and one can prove that 
$\lim_{\epsilon \to 0} E = \frac{1}{2}\gamma |\partial \Omega|$.
In other words, because of the introduction of granule boundaries,
interfacial energy enters the problem even in the linear case.
We are confident
that~\eqref{eq:RBT}--\eqref{eqn:stressbalance} is a correct description
of long-range interactions between granule surfaces.

@@

\subsection{Applications}
Since the formulation is scale independent, it can be applied broad
range of nonspecific self-organization phenomena in surface chemistry,
biology and engineering. For one, the
formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
the right behavior expected from amphiphilic self-assembly.
For example,
three bodies with amphiphilic label (\S\ref{sec:specific_aim1})
spontaneously self-organize to sequester the hydrophobic fluid phase
(the red phase in Figure~\ref{fig:flow_map}).
Moreover, a simple change
of boundary conditions from amphiphilic,
to biased hydrophobic, to polar
results in distinct equilibrium morphologies
(Figure~\ref{fig:self-assembly2}).
Some further applications are
(i) Chemistry: Janus spheres Since
the formulation is scale independent, it can represent a suspension of
amphiphiles, where the granules represent the mean properties of a small
collection of lipids, at the nanoscopic scale. For larger scales, the
representation is literal and the granules Janus spheres.
(ii) Pickering emulsion
(iii) \todo[inline]{Bertozzi's problem}
(iv) Tension driven microprinting
(v) Vesicle hydrodynamics.

### 2022-11-12 NSF2022/Description/specificaim1v2.tex
BG mods

In the double-well potential case, \eqref{eqn:phase}
is a nonlinear Allen-Cahn
equation.
This situation models granules immersed in a two-phase fluid
(e.g. granules in an emulsion) 
where there is an interesting interplay
(1) the long-range alignment of granules with (2) 
the diffusive interface energy of the free boundary
between fluid phases.
On unbounded domains like $\Omega(t)$,
Allen-Cahn equations can have multiple of solutions
\cite{Alama1997StationaryLS,Alikakos2008OnAE,Bronsard1993OnTB,
  Byeon2014SolutionsOH, Byeon2013OnAP, Alessio2005ENTIRESI,
  Trumper2007ExistenceOA} and so we must reformulate
\eqref{eqn:phase} so that $\phi$ is well-defined.
A natural modification changes
\eqref{eqn:phase} to an initial value problem with
transport by the background fluid;
\begin{equation}
  \label{eqn:phase_transport}
  \phi_t + \uu \cdot \nabla
  = -\lambda \frac{\delta E}{\delta \phi}
  =  \lambda(\epsilon^2 \Delta \phi - W'(\phi)),
  \quad \phi(\xx,0) = \phi_0(\xx),
\end{equation}
for initial data $\phi_0$.
The modified systems enjoys energy law similar to \eqref{eq:energy_law} 
with an addtional dissipation term involving the square 
the Euler-Lagrange derivative $\frac{\delta E}{\delta \phi}$ and dampening factor $\lambda > 0$.
There are several works dealing with the
geometric characterization of the geometric evolution
of interfaces under the Allen-Cahn and Cahn-Hilliard equations
\cite{Christlieb2019CompetitionAC, Gavish2011CurvatureDF, Dai2019WeakSF,
  Promislow2017ExistenceBA, Dai2015CompetitiveGE, Promislow2012CriticalPO,
  Dai2022GeometricEO, Dai2020MinimizersFT,Dai2013GeometricEO,Promislow2022UndulatedBI} and
well-posedness when coupled to flow in static domains
\cite{Jiang2017TwophaseIF, Liu2012StrongSF, Giorgini2019WellPosednessOA,
Wu2022WellposednessOA, Gal2010AsymptoticBO,
Giorgini2020DiffuseIM,Giorgini2019UniquenessAR}.
The proposed research extends these results to
problems with moving domains.

>>>>

In the double-well potential case, \eqref{eqn:phase}
is a nonlinear Allen-Cahn
equation.
This situation models granules immersed in a two-phase fluid
(e.g. granules in an emulsion) 
where there is an interesting interplay
(1) the long-range alignment of granules with (2) 
the diffusive interface energy of the free boundary
between fluid phases.
On unbounded domains like $\Omega(t)$,
Allen-Cahn equations can have multiple of solutions
\cite{Alama1997StationaryLS,Alikakos2008OnAE,Bronsard1993OnTB,
  Byeon2014SolutionsOH, Byeon2013OnAP, Alessio2005ENTIRESI,
  Trumper2007ExistenceOA,Benci2019MultipleSF}
and so we must reformulate
\eqref{eqn:phase}.
A natural modification changes
\eqref{eqn:phase} to an initial value problem with
transport by the background fluid;
\begin{equation}
  \label{eqn:phase_transport}
  \phi_t + \uu \cdot \nabla
  = -\lambda \frac{\delta E}{\delta \phi}
  =  \lambda(\epsilon^2 \Delta \phi - W'(\phi)),
  \quad \phi(\xx,0) = \phi_0(\xx),
\end{equation}
for initial data $\phi_0$.
The modified systems enjoys energy law similar to \eqref{eq:energy_law} 
with an addtional dissipation term involving the square 
the Euler-Lagrange derivative $\frac{\delta E}{\delta \phi}$ and dampening factor $\lambda > 0$.
There are several works dealing with the
geometric characterization of the geometric evolution
of interfaces under the Allen-Cahn and Cahn-Hilliard equations
\cite{Christlieb2019CompetitionAC, Gavish2011CurvatureDF, Dai2019WeakSF,
  Promislow2017ExistenceBA, Dai2015CompetitiveGE, Promislow2012CriticalPO,
  Dai2022GeometricEO, Dai2020MinimizersFT,Dai2013GeometricEO,Promislow2022UndulatedBI} and
well-posedness when coupled to flow in static domains
\cite{Jiang2017TwophaseIF, Liu2012StrongSF, Giorgini2019WellPosednessOA,
Wu2022WellposednessOA, Gal2010AsymptoticBO,
Giorgini2020DiffuseIM,Giorgini2019UniquenessAR}.
The proposed research extends these results to
problems with moving domains.
